Correlation between different emission channels from an atom inside a leaky driven cavity

### 2019-12-17 newpaper.tex
Cambios de pablo al texto

This article is organized as follows: A general overview of the
theoretical model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain join probability distribution
of the the number of spontaneous and cavity emissions. In section
\ref{sc:correlation} we calculate the correlation between the two
variables. Concluding remarks are given in section
\ref{sc:conclusions}
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{A driven atom in free space (a) and inside a driven leaky
  cavity (b). Each time the atom decays, it emits a photon. In each
  case, we count the number of photons $m$ and $n$, emitted in two
  different directions respectively. For the atom in free space there
  is no correlation between $m$ and $n$. For the atom inside the leaky
  cavity we find a correlation between $m$ and $n$.}
\end{center}
\end{figure*}
\end{center}

@@

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps correponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm. \ref{alg1}.

@@

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we calculate the probability distribution of the
number of spontaneous emissions, $n_s$, under different conditions.
First we calculate the distribution probability of $n_s$ when we know
the number of leaked photons from the cavity, $n_c$; we use
$p(n_s|n_c)$ to denote the distribution. Using this function we can
investigate the correlation between $n_s$ and $n_c$ as a function of
the cavity decay rate. This correlation is a measure of how much
information we can obtain about $n_s$ if we know $n_c$.

@@

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. For
the case of the driven Jaynes-Cummings system, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}
\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.7]{newerrorppp.pdf}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons in
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

\paragraph{The case when the number of photons leaked from the cavity  is known}
\fxnote{No esta claro que hiciste aqui. Segun yo corriste el programa
  distinto tiempo para cada caso}
We calculate the distribution probability of the number of spontaneous
emission conditioned to the number of photons detected leaking the
cavity. We assume that the mean flux of photons in each channel is
known in advance (they can be calculated knowing the cavity drive).
The results are shown in Fig.\ref{probdiss}. As the number of leaked
photons increases, the mean number of spontaneous emissions increases.
This result is expected, because the number of leaked photons is
correlated with the time we are counting spontaneus emission photons
from a driven atom: the larger the number of leaked photons the larger
the time we measure spontaneous emitted photons which implies a larger
mean number of emitted photons. Also, the probability distribution is
wider when the number of leaked photons increases, this implies less
accuracy guessing the number of spontaneus emission as the number of
leaked photons increases. If we know the cavity drive, this results
does not imply that we can learn something extra about the number of
spontaneous emissions knowing the number of photons leaked from the
cavity; it is clear that when we increase the time window where we
count photons, both, the number of leaked photons and the number of
spontaneous emissions, increases.

@@

\begin{figure}[!b]  
\centering
\includegraphics[scale = 0.5]{newsigmaengg.pdf}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure}

\paragraph{The case where the time we measure photons is fixed}

We know fix the time we measure photons, which is equivalente to
fixing the mean number of spontaneous emited photons or the mean number
of leaked photons from the cavity.

We focus in the case where we fix the mean number of photons inside
the cavity. This number depends on the cavity drive and the atomic
parameters.

Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

@@

\begin{center}
\begin{figure*}[!t]
\begin{center}
\includegraphics[scale = 0.7]{lastgraph1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500. (a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.

>>>>

This article is organized as follows: A general overview of the
theoretical model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain join probability distribution
of the the number of spontaneous and cavity emissions. In section
\ref{sc:correlation} we calculate the correlation between the two
variables. Concluding remarks are given in section
\ref{sc:conclusions}
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{A driven atom in free space (a) and inside a driven leaky
  cavity (b). We count the number of photons $m$ and $n$, emitted by
  the atom in two different directions. For the atom in free space
  there is no correlation between $m$ and $n$. For the atom inside the
  leaky cavity we find a correlation between $m$ and $n$.}
\end{center}
\end{figure*}
\end{center}

@@

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{Probability distribution of spontaneous emissions for
  different number of cavity photons. Parameters $\mathcal{E}  =
  \kappa = \gamma = g = 1$, $100,000$ quantum trajectories. } \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps correponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm. \ref{alg1}.

@@

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we calculate the probability distribution of the
number of spontaneous emissions $n_s$, under two different conditions.
First, we study the distribution probability of $n_s$ when we consider
the set of quantum trajectories where the number of leaked photons
from the cavity is $n_c$. This simulate the physical situation where
we count the number of spontaneus photons until the moment where the
number of leaked photons from the cavity is $n_c$. It is impossible to
know in advance how long it takes to the cavity to leak $n_c$ photons,
thus the time each quantum trajectory is evolved is not fixed. Second,
we fix the time each quantum trajectory is evolved and count the
number of spontaneus emissions $n_s$, and cavity emissions $n_c$. From
the set of quantum trajectories evolved a fixed time, we calculate the
joint probability $p(n_s,n_c)$, of finding $n_s$ spontaneous emissions
and $n_c$ cavity emissions. Using $p(n_s,n_c)$ we calculate the
correlations between the two random variables. This correlation is a
measure of how much information we can obtain about $n_s$ if we know
$n_c$.

@@

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. For
the case of the driven Jaynes-Cummings system, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}

\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons in
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

\subsection{Quantum trajectories with fixed number of photons leaked from the cavity}
We calculate the distribution probability of the number of spontaneous
emission when a fixed number of photons leaked the cavity. We assume
that the mean number of photons inside the cavity is $1/9$. The
results are shown in Fig.~\ref{probdiss}. As the number of leaked
photons increases, the mean number of spontaneous emissions increases.
This result is expected, because the number of leaked photons is
correlated with the time we are counting spontaneus emission photons
from a driven atom: the larger the number of leaked photons the larger
the time we measure spontaneous emitted photons, which implies a
larger mean number of emitted photons. Also, as shown in
Fig~\ref{graph}, the probability distribution is wider as the number
of leaked photons increases, this implies less accuracy guessing the
number of spontaneus emission. If we know the cavity drive, this
results does not imply that we can learn something extra about the
number of spontaneous emissions knowing the number of photons leaked
from the cavity; it is clear that when we increase the time window
where we count photons, both, the number of leaked photons and the
number of spontaneous emissions, increases.

@@

\begin{figure}[!h]  
\centering
\includegraphics[scale = 0.5]{newsigmaeng.pdf}
\caption{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}
\label{graph}
\end{figure}

\subsection{Quantum trajectories with fixed duration}
We consider the set of quantum trajectories of the same duration. This
corresponds to fixing the time we measure photons. Each set of quantum
trajectories with the same duration is labelled with its mean number
of spontaneous emitted photons $\mu$. We consider the case where we
fix the mean number of photons inside the cavity to $1$. As shown by
Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
atomic parameters.

In Fig.~\ref{error2}(a) the probability distribution of spontaneous
emitted photons is shown for different mean values. As it is shown in
Fig.~\ref{error2}(b), the width of the distribution increases linearly
with the mean number of spontaneus emission. This behaviour does not
imply any correlation between the number of spontaneus emissions and
cavity emissions.

Now we focus in the case, where given a set of quantum trajectories
with fixed duration, we postselect all the trajectories where the
number of cavity emissions is a fixed number $n_c$, and plot
$p(n_s|n_c)$, the probability distribution of the number of spontaneus
emissions $n_s$, under the condition that $n_c$ cavity emissions
happened. If $p(n_s|n_c)\neq p(n_s)p(n_c)$, $n_s$ and $n_c$ are not
independent: information can be extracted about $n_s$ knowing $n_c$.
In Fig.~\ref{probdisult} (a) we show the probability distribution of
$n_s$ for the case where $n_c$.

In Fig.~\ref{probdisult} (b), where we obtain a variance almost equal
to the mean value, something which is characteristic of Poisson
distributions.

\begin{center}
\begin{figure*}[!t]
\includegraphics[scale = 0.7]{newerrorppp.pdf}
\caption{(a) Probability distributions for different mean number of
  spontaneous emissions $\mu$; (b) Calculation of variance with
  respect to the mean number of sponatenous emissions $\mu$. In both
  cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ ,
  $\kappa = g = 0.1$ and
  $\mathcal{E} = \kappa |\langle n \rangle|[1 + 2g^2/\gamma
  \kappa]$.} \label{error2}
\end{figure*}
\end{center}

\begin{center}
\begin{figure*}
\begin{center}
\includegraphics[scale = 0.7]{lastgraph1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500. (a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

@@

The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.
